The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-03 analysis/paper/paper.qmd
Write geocoded data frame to file

```{r extract-pdf-text}
#| echo: false
#| cache: true

data_path <- here("analysis", "data", "derived_data", "emu_theses_with_text.csv")

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu_theses$text <- convert_pdf_text(pdf_paths)
  write_csv(emu_theses, data_path)
} else {
  emu_theses$text <- read_csv(data_path)$text
}

>>>>

```{r get-pdf-text}
#| echo: false
#| cache: true

data_path <- here("analysis", "data", "derived_data", "emu_theses_with_text_and_location.csv")

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu_theses$text <- convert_pdf_text(pdf_paths)

  # Write thesis dataframe to file
  write_csv(emu_theses, data_path)
} else {
  emu_theses$text <- read_csv(data_path)$text
  emu_theses$longitude <- read_csv(data_path)$longitude
  emu_theses$latitude <- read_csv(data_path)$latitude
}
